---
title: "Comparison Samples"
output: html_notebook
---

## Looking at differences between samples

```{r}
library(sashaUseful)
library(tidyverse)
mySample <- readRDS(here('data/sample_1000_test.RDS'))
mySample2 <- readRDS(here("data/sample_WP_algo_500.RDS"))

```

##Compare ranges
```{r}
mySample$pageId %>% range() %>% .mf()
mySample2$pageId %>% range() %>% .mf()
```

### Compare SD / mean / range
```{r}
mySample %>% 
  group_by(pageId) %>% 
  summarize(contrib = n()) %>% 
  pull(contrib) -> tmp
range(tmp)
mean(tmp)
sd(tmp)
mySample2 %>% 
  group_by(pageId) %>% 
  summarize(contrib = n()) %>% 
  pull(contrib) -> tmp
range(tmp)
mean(tmp)
sd(tmp)

```

## Reduce range to the one for WP
```{r}
mySample %>% 
  filter(pageId>123000, pageId <998492) %>% 
  group_by(pageId) %>% 
  summarize(contrib = n()) %>% 
  pull(contrib) -> tmp
range(tmp)
mean(tmp)
sd(tmp)
```

No discernable difference, so what is the problem?

```{r}
mySample %>% 
  group_by(pageId) %>% 
  summarize(contrib = n()) %>% 
  ggplot(aes(contrib))+geom_density()
```
```{r}
mySample2 %>% 
  group_by(pageId) %>% 
  summarize(contrib = n()) %>% 
  ggplot(aes(contrib))+geom_density()
```

let's pull the first 10 ids and see
```{r}
myPageIds <- mySample$pageId %>% unique
mySample %>% 
  filter(pageId %in% myPageIds[1:20]) %>% 
  group_by(pageId) %>% 
  summarize(contrib = n()) %>% 
  ggplot(aes(contrib))+geom_density()
  
```
```{r}
mySample %>% 
  filter(pageId %in% myPageIds[1:20]) %>% 
  pull(pageId) %>% unique
```

OK, finding nothing here. 

```{r}
library(lubridate)
mySample$Date <- as.Date(mySample$timestamp)
mySample %>% 
  ggplot(aes(Date)) + geom_density()
mySample2$Date <- as.Date(mySample2$timestamp)
mySample2 %>% 
  ggplot(aes(Date)) + geom_density()


```

```{r}
mySample2$source <- "WP algo"
mySample$source <- "MY algo"
rbind(mySample,mySample2) ->allData
allData%>% 
  ggplot(aes(Date, color=source)) + geom_density()
```


Let's take a look at all data in a scatterplot

```{r}
allData %>% 
  group_by(source,pageId,Date) %>% 
  summarize(n=n()) %>% 
  ggplot(aes(Date,n,color=source))+geom_point()+
  geom_smooth()

```

```{r}
allData %>% 
  group_by(source,pageId,Date) %>% 
  summarize(n=n()) %>% 
  ggplot(aes(Date,n,color=source))+
  #geom_point()+
  geom_smooth(method='lm')+
  geom_smooth()
```

Manual inspection seems to indicate that my sample contains talk-pages as well as articles. Let's reload the original data and see.
```{r}

```

