---
title: "Notes 2019-05-22"
output: html_notebook
---


## Analysis of Baselines

```{r}
library(tidyverse)
library(ggpmisc)
library(useful)
library(here)

  myData <- 
    readRDS( here("data/sample_1000_contributions_ca.RDS") ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_en.RDS"))
    ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_eo.RDS"))
    ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_es.RDS"))
    ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_eu.RDS"))
    ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_gl.RDS"))
    ) %>% 
   rbind(
     readRDS( here("data/sample_1000_contributions_fr.RDS"))
  ) %>%
    rbind(
      readRDS( here("data/sample_1000_contributions_pt.RDS"))
    )  
```

```{r}
names(myData)
```

```{r}
myData %>% 
  group_by(domain) %>%
  summarize(
    N = n()
    )
```

```{r}
myData %>% 
  group_by(domain) %>% 
  summarize(N=n()) %>% 
  ggplot(aes(fct_reorder(domain, N, .desc = TRUE),N/1000))+
  geom_bar(stat='identity')+
  ylab("Mean # of Edits")+
  xlab("Language Code")+
  ggtitle("Mean Number of Edits per Page", "Random Sample of ~1000 per Language ")
```

## Users of These Languages (L1 and L2)
```{r}
speakers <- tribble(
  ~Language, ~Speakers, ~Type,
  "es", 580000000L, "L1",
  "en", 400000000L, "L1",
  "fr", 76800000L,  "L1",
  "pt", 203000000L, "L1",
  "ca", 4100000L,   "L1",
  "gl", 1500000L,   "L1",
  "eu", 750000,     "L1",
  "eo", 2000L,      "L1",
  "es", 125000000L, "L2",
  "en", 750000000L, "L2",
  "fr", 200000000L, "L2",
  "pt", 20000000L,  "L2",
  "ca", 5900000L,  "L2",
  "gl", 900000L,    "L2",
  "eu", 350000,     "L2",
  "eo", 1000000L,   "L2"
)
# speakers <- data.frame(
# L1 = c(es = 580000000L, en = 400000000L, fr=76800000L,  pt = 203000000L, ca = 4100000L, gl = 1500000L, eo = 2000L),
# L2 = c(es = 125000000, en = 750000000, fr = 200000000, pt = 20000000, ca = 5900000, gl = 900000, eo = 1000000)
# )


```

```{r}
speakers$Language <- fct_reorder(speakers$Language,speakers$Speakers,fun = sum, .desc=TRUE)
speakers %>% 
  ggplot(aes(Language,Speakers,fill=Type))+
  geom_bar(stat='identity', position = 'dodge')+
  scale_y_continuous(labels=function(x)useful::multiple(x,'M'))+
  xlab("Language Code")
```

### Smaller languages
```{r}
speakers %>% 
  filter(Speakers <20000000L) %>% 
  ggplot(aes(Language,Speakers,fill=Type))+
  geom_bar(stat='identity', position = 'dodge')+
  scale_y_continuous(labels=function(x)useful::multiple(x,'M'))+
  xlab("Language Code")
```


##Variability

```{r}
myData %>% 
  group_by(domain, pageId) %>% 
  summarize(N=n()) %>% 
  ggplot(aes(N, color=domain))+geom_density()
  
```

```{r}
last_plot()+
  facet_wrap(~domain)
```

## Age of Wikipedia
```{r}
myData %>% 
  group_by(domain) %>% 
  summarize(
    First = min(range(timestamp,na.rm = TRUE)) %>% as.Date(),
    Last = max(range(timestamp,na.rm = TRUE)) %>% as.Date()
    )
```

Not really that interesting

## Example of Information Available
```{r}
myData %>% 
  head(10)
```

## Distribution of Contribution (2)
```{r}
myData %>% 
  group_by(pageId) %>% 
  summarize(N=n())->mySummary1
mySummary1 %>% 
  ggplot(aes(N))+
  geom_density()
```

```{r}
gg2 <- mySummary1 %>% filter(N>450) %>% 
  ggplot(aes(N))+geom_density()
gg2
```

```{r}

p<-mySummary1 %>% 
  ggplot(aes(N))+
  geom_density()

data.tb <- tibble(x = 1, y = 1, 
                  plot = list(gg2 +
                                theme_bw(8)))

p+
  expand_limits(x = 0, y = 0) +
  geom_plot_npc(data = data.tb, aes(npcx = x, npcy = y, label = plot))+
  annotate("segment", xend = 500 , yend = 0.002, x = 450, y = .02,arrow=arrow(), color='red')

```

The reason for this *bump* is due to the fact the API only stores the last 500 revisions. 


```{r}
mySummary1 %>% 
  filter(N>100) %>% 
  ggplot(aes(N))+geom_histogram(binwidth = 10)+
  ggtitle("Edits per Page > 100")
```

As a result *frequency of edits* may be a better measure.

## Frequency of Edits

* Unit: Edits / Day
* Equivalent to: 11.6 µHz (microhertz)

```{r}
#Calculate range of contributions for each page
myData %>% 
  group_by(domain,pageId) %>% 
  summarize(
    N = n(),
    Min.Date = min(timestamp) %>% as.Date() %>% as.numeric,
    Max.Date = max(timestamp) %>% as.Date() %>% as.numeric
  ) %>% 
  mutate(Date.Range = Max.Date - Min.Date) %>% 
  mutate(Edits.per.Day = N/(Date.Range)) ->
  mySummary2
```

```{r}
mySummary2 %>% 
  ggplot(aes(Edits.per.Day))+geom_histogram(binwidth = 1)+
  ggtitle("Edits per Day")

```

```{r}
smallN <- mySummary2 %>% 
  filter(Edits.per.Day > 1) %>% nrow()
bigN <- mySummary2 %>% nrow
mySummary2 %>% 
  filter(Edits.per.Day > 1) %>% 
  ggplot(aes(Edits.per.Day))+geom_histogram(binwidth = 1)+
  ggtitle("Edits per Day > 1 ",str_glue("{smallN} /  {bigN} ≈ {round(smallN/bigN, digits=4)*100}%"))

```

## The Wiki Articles 
```{r}
wikiContribs <- readRDS(here('data/wikiPages_Catalonia_referendum_contribs_2.RDS'))
#Calculate range of contributions for each page
wikiContribs %>% 
  group_by(domain,pageId) %>% 
  summarize(
    N = n(),
    Min.Date = min(timestamp) %>% as.Date(),
    Max.Date = max(timestamp) %>% as.Date(),
    Mean.size = mean(as.numeric(size)),
    Median.size = median(as.numeric(size)),
    SD.size = sd(as.numeric(size))
  ) %>% 
  mutate(Date.Range = Max.Date %>% as.numeric - Min.Date %>% as.numeric) %>% 
  mutate(Edits.per.Day = N/(Date.Range)) %>% 
  mutate(Size.Change.per.Day = Mean.size/Date.Range)->
  mySummary3
```

```{r}
mySummary3 %>% 
  ggplot(aes(fct_reorder(domain,desc(Edits.per.Day) ), Edits.per.Day))+
  geom_bar(stat='identity')+
  ggtitle("Edits per Day, Nine Wikipedia Pages on Catalonian Independence")+
  xlab("Language Code")
```

## Size Change
```{r}
mySummary3 %>% 
  ggplot(aes(fct_reorder(domain,desc(Size.Change.per.Day) ), Size.Change.per.Day))+
  geom_bar(stat='identity')+
  ggtitle("Edits per Day, Nine Wikipedia Pages on Catalonian Independence")+
  xlab("Language Code")
```

## Summary Data
```{r}
mySummary3 %>% 
  knitr::kable()
```

## Timelines
```{r}
wikiContribs <- wikiContribs %>% 
  mutate(Date = as.Date(timestamp))

  wikiContribs %>% 
   # group_by(Date, domain) %>% 
    group_by(Date) %>% 
    summarize(N=n()) %>% 
    ggplot(aes(Date,N))+
    geom_line(stat='identity')+
    ggtitle("Edits per Day") -> gg2
```

```{r}
#gg2 <-  
  gg2+
  annotate('segment',xend=as.Date('2017-10-05'),x=as.Date("2017-12-01"), yend=100,y=110, color='red', arrow=arrow(length=unit(.1,'inches')))+
  annotate('text',x=as.Date("2017-12-01"), y=112, label='October 1st',hjust=0)+
  annotate('text',x=as.Date("2017-12-01"), y=107, label='Independence Referendum',hjust=0)
  
 # gg2
  
```

## Zooming in

```{r}
focussed <- wikiContribs %>% 
  filter(Date >= '2017-09-01',
         Date <= '2018-02-28') %>% 
   # group_by(Date, domain) %>% 
    group_by(Date) %>% 
    summarize(N=n())
```

## Zooming in (2)
```{r}
myDateSeq <- seq.Date(min(focussed$Date), max(focussed$Date), by='7 days')
focussed %>% 
  ggplot(aes(Date,N)) +
  geom_line()+
  scale_x_date(date_breaks='1 month',date_labels='%b')+
  annotate('text',x=myDateSeq,y=-1,label=format.Date(myDateSeq,"%d"), color='red',alpha=.7, cex=2) -> gg3

gg3
  


```

```{r}
gg3+annotate('segment',xend=as.Date('2017-10-05'),x=as.Date("2017-11-01"), yend=100,y=110, color='red', arrow=arrow(length=unit(.1,'inches')))+
  annotate('text',x=as.Date("2017-11-01"), y=112, label='October 1st',hjust=0)+
  annotate('text',x=as.Date("2017-11-01"), y=107, label='Independence Referendum',hjust=0) ->gg4

gg4
```

```{r}
gg4 + annotate('segment',xend=as.Date('2017-10-28'),x=as.Date("2017-11-27"), yend = 50,y = 60, color='red', arrow=arrow(length=unit(.1,'inches')))+
  annotate('text',x=as.Date("2017-11-28"), y=63, label='Indepencence Declared',hjust=0)+
  annotate('text',x=as.Date("2017-11-28"), y=58, label='Self-Government Suspended',hjust=0) -> gg5
gg5
```

```{r}
gg5 + annotate('segment',xend=as.Date('2018-01-08'),x=as.Date("2018-02-01"), yend = 40,y = 50, color='red', arrow=arrow(length=unit(.1,'inches')))+
  annotate('text',x=as.Date("2018-02-01"), y=50, label='Three Kings Day',hjust=0)+
  annotate('text',x=as.Date("2018-02-01"), y=45, label='(Reyes)',hjust=0)

  
```

## By Domain
```{r}
focussed2 <- wikiContribs %>% 
  filter(Date >= '2017-09-01',
         Date <= '2018-02-28') %>% 
   # group_by(Date, domain) %>% 
    group_by(Date, domain) %>% 
    summarize(N=n())
focussed2 %>%  
  ggplot(aes(Date,N,color=domain))+
  geom_line()
  
```

```{r}
myEvents <- tribble(~Event,~Date,
                    "Referendum",as.Date('2017-10-01'),
                    "155",as.Date('2017-10-27'),
                    "Reyes",as.Date('2018-01-08'),
                    )
focussed2 %>% 
  #filter(domain %in% c("ca","en","es","eu", "fr")) %>% 
  ggplot(aes(Date,N))+geom_line()+
# +
   geom_point(aes(Date,40), data=myEvents)+
   facet_wrap(~domain,ncol=1)
```

```{r}
focussed2 %>% 
  filter(domain %in% c("ca","en","es","eu", "fr")) %>% 
  ggplot(aes(Date,N))+geom_line()+
# +
   geom_point(aes(Date,40), data=myEvents)+
   facet_wrap(~domain,ncol=1)
```

