---
title: "Notes 2019-05-22"
output: html_notebook
---


## Analysis of Baselines

```{r}
library(tidyverse)
library(ggpmisc)
library(useful)
library(here)

  myData <- 
    readRDS( here("data/sample_1000_contributions_ca.RDS") ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_en.RDS"))
    ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_eo.RDS"))
    ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_es.RDS"))
    ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_eu.RDS"))
    ) %>% 
    rbind(
      readRDS( here("data/sample_1000_contributions_gl.RDS"))
    ) %>% 
   rbind(
     readRDS( here("data/sample_1000_contributions_fr.RDS"))
  ) %>%
    rbind(
      readRDS( here("data/sample_1000_contributions_pt.RDS"))
    )  
```

```{r}
names(myData)
```

```{r}
myData %>% 
  group_by(domain) %>%
  summarize(
    N = n()
    )
```

```{r}
myData %>% 
  group_by(domain) %>% 
  summarize(N=n()) %>% 
  ggplot(aes(fct_reorder(domain, N, .desc = TRUE),N/1000))+
  geom_bar(stat='identity')+
  ylab("Mean # of Edits")+
  xlab("Language Code")+
  ggtitle("Mean Number of Edits per Page for a Random Sample of 1000")
```

## Users of These Languages (L1 and L2)
```{r}
speakers <- tribble(
  ~Language, ~Speakers, ~Type,
  "es", 580000000L, "L1",
  "en", 400000000L, "L1",
  "fr", 76800000L,  "L1",
  "pt", 203000000L, "L1",
  "ca", 4100000L,   "L1",
  "gl", 1500000L,   "L1",
  "eu", 750000,     "L1",
  "eo", 2000L,      "L1",
  "es", 125000000L, "L2",
  "en", 750000000L, "L2",
  "fr", 200000000L, "L2",
  "pt", 20000000L,  "L2",
  "ca", 5900000L,  "L2",
  "gl", 900000L,    "L2",
  "eu", 350000,     "L2",
  "eo", 1000000L,   "L2"
)
# speakers <- data.frame(
# L1 = c(es = 580000000L, en = 400000000L, fr=76800000L,  pt = 203000000L, ca = 4100000L, gl = 1500000L, eo = 2000L),
# L2 = c(es = 125000000, en = 750000000, fr = 200000000, pt = 20000000, ca = 5900000, gl = 900000, eo = 1000000)
# )


```

```{r}
speakers$Language <- fct_reorder(speakers$Language,speakers$Speakers,fun = sum, .desc=TRUE)
speakers %>% 
  ggplot(aes(Language,Speakers,fill=Type))+
  geom_bar(stat='identity', position = 'dodge')+
  scale_y_continuous(labels=function(x)useful::multiple(x,'M'))+
  xlab("Language Code")
```

### Smaller languages
```{r}
speakers %>% 
  filter(Speakers <20000000L) %>% 
  ggplot(aes(Language,Speakers,fill=Type))+
  geom_bar(stat='identity', position = 'dodge')+
  scale_y_continuous(labels=function(x)useful::multiple(x,'M'))+
  xlab("Language Code")
```


##Variability

```{r}
myData %>% 
  group_by(domain, pageId) %>% 
  summarize(N=n()) %>% 
  ggplot(aes(N, color=domain))+geom_density()
  
```

```{r}
last_plot()+
  facet_wrap(~domain)
```

## Age of Wikipedia
```{r}
myData %>% 
  group_by(domain) %>% 
  summarize(
    First = min(range(timestamp,na.rm = TRUE)) %>% as.Date(),
    Last = max(range(timestamp,na.rm = TRUE)) %>% as.Date()
    )
```

Not really that interesting

## Example of Information Available
```{r}
myData %>% 
  head(10)
```

## Distribution of Contribution (2)
```{r}
myData %>% 
  group_by(pageId) %>% 
  summarize(N=n())->mySummary1
mySummary1 %>% 
  ggplot(aes(N))+
  geom_density()
```

```{r}
gg2 <- mySummary1 %>% filter(N>450) %>% 
  ggplot(aes(N))+geom_density()
gg2
```

```{r}

p<-mySummary1 %>% 
  ggplot(aes(N))+
  geom_density()

data.tb <- tibble(x = 1, y = 1, 
                  plot = list(gg2 +
                                theme_bw(8)))

p+
  expand_limits(x = 0, y = 0) +
  geom_plot_npc(data = data.tb, aes(npcx = x, npcy = y, label = plot))+
  annotate("segment", xend = 500 , yend = 0.002, x = 450, y = .02,arrow=arrow(), color='red')

```

The reason for this *bump* is due to the fact the API only stores the last 500 revisions. 


```{r}
mySummary1 %>% 
  filter(N>100) %>% 
  ggplot(aes(N))+geom_histogram(binwidth = 10)+
  ggtitle("Edits per Page N > 100")
```

As a result *frequency of edits* may be a better measure.

## Frequency of Edits

* Unit: Edits / week 

```{r}
#Calculate range of contributions for each page
myData %>% 
  group_by(domain,pageId) %>% 
  summarize(
    N = n(),
    Min.Date = min(timestamp) %>% as.Date() %>% as.numeric,
    Max.Date = max(timestamp) %>% as.Date() %>% as.numeric
  ) %>% 
  mutate(Date.Range = Max.Date - Min.Date) %>% 
  mutate(Edits.per.Day = N/(Date.Range)) ->
  mySummary2
```

```{r}
mySummary2 %>% 
  ggplot(aes(Edits.per.Day))+geom_histogram(binwidth = 1)+
  ggtitle("Edits per Day")

```

```{r}
smallN <- mySummary2 %>% 
  filter(Edits.per.Day > 1) %>% nrow()
bigN <- mySummary2 %>% nrow
mySummary2 %>% 
  filter(Edits.per.Day > 1) %>% 
  ggplot(aes(Edits.per.Day))+geom_histogram(binwidth = 1)+
  ggtitle("Edits per Day > 1 ",str_glue("{smallN} /  {bigN} ={round(smallN/bigN, digits=3)*100}%"))

```

